EuPPollNet: A European database of plant-pollinator networks

### 2024-09-21 Manuscript/EuPPollNet_Ms.qmd
Affiliations update

Consistent with @olesen2002, we find that residual connectance (i.e., the deviation from the expected connectance for a given network size) was lower at higher latitudes, while normalised nestedness increased towards higher latitudes. Networks at lower latitudes in Europe are exposed to higher temperatures, which can result in higher visitation rates [@arroyo1985; @classen2015; @herrera2019], and the overall level of pollinator generalization is known to be higher at lower latitudes [@schleuning2012]. These factors should increase the number of possible connections that can be established between plants and pollinators for a given network size, resulting in more connected and less nested networks at lower latitudes in Europe. Finally, most empirical networks (~85%) showed a non-nested structure. This result opposes to the idea that plant-pollinator networks tend to be nested [@bascompte2003], and support recent findings showing that nestedness is not a prevalent feature in plant-pollinator networks [@payrato2019].

@@

We thank all the taxonomist and ecologist that has made this database possible by contributing with their fieldwork data.

@@

>>>>

Consistent with @olesen2002, we find that residual connectance (i.e., the deviation from the expected connectance for a given network size) was lower at higher latitudes, while normalised nestedness increased towards higher latitudes. Networks at lower latitudes in Europe are exposed to higher temperatures, which can result in higher visitation rates [@arroyo1985; @classen2015; @herrera2019], and the overall level of pollinator generalization is known to be higher at lower latitudes [@schleuning2012]. These factors should increase the number of possible connections that can be established between plants and pollinators for a given network size, resulting in more connected and less nested networks at lower latitudes in Europe. Finally, most empirical networks (~85%) showed a non-nested structure. This result contrasts with earlier work suggesting that plant-pollinator networks are typically nested [@bascompte2003] and it aligns with recent evidence showing that nestedness is not a common feature in plant-pollinator networks [@payrato2019].

@@

We thank all the taxonomists and ecologists that has made this database possible by contributing with their fieldwork data.

@@

- Figure S5
